Simulations

### 2017-11-17 3-simus.Rmd
save

```{r}
if (!dir.exists("results2")) dir.create("results2")

@@

>>>>

```{r, eval=TRUE}
if (!dir.exists("results2")) dir.create("results2")

@@

```{r, eval=FALSE}
if (!dir.exists("results3")) dir.create("results3")

G6 <- big_copy(G, ind.col = which(CHR == 6))
ind.HLA6 <- snp_indLRLDR(CHR[CHR == 6], POS[CHR == 6], subset(LD.wiki34, ID == "hild12"))

  res.file <- paste0("results3/simu_", i, ".rds")
  if (file.exists(res.file)) next

  # Simulate phenotypes
  pheno.all <- get_pheno(
    G6,    
    h2 = params[["par.h2"]], 
    M = as.integer(par.causal[1]), 
    ind.possible = `if`(par.causal[2] == "all", cols_along(G6), ind.HLA6),
    effects.dist = params[["par.dist"]], 
    model = params[["par.model"]], 
    K = 0.3                 
  )

  # Get results from all methods
  res <- bind_rows(
    PRS(G6, CHR[CHR == 6], POS[CHR == 6], pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G6, pheno.all, covar.all, ind.train, ind.test, "logit-simple")
  )
  print(res)
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```
